\documentclass[12pt]{article}
\usepackage{enumitem, txfonts}
\usepackage[paper=a4paper,
	%includefoot, % Uncomment to put page number above margin
	marginparwidth=1in,	% Length of section titles
	marginparsep=.05in,	% Space between titles and text
	margin=1in, top=1in, bottom=1in,
]{geometry}
\usepackage[
	colorlinks, anchorcolor=blue, citecolor=blue, linkcolor=blue, urlcolor=blue,
	bookmarksdepth=1
]{hyperref}
\urlstyle{same}
\usepackage{fancyhdr}
	\pagestyle{fancy}
\usepackage[compact]{titlesec}
	\titleformat{\section}{\large\bf}{}{}{}
\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{lastUpdated}{
	\rhead{Curriculum Vitae. \today}
}

\setlength{\parindent}{0pt}

\begin{document}
\thispagestyle{lastUpdated}
\section*{\Large Kuan-Wen Lai}
	Institute of Mathematics, Academia Sinica\\
	6F, Astronomy-Mathematics Building\\
	No. 1, Sec. 4, Roosevelt Road, Taipei 106319, Taiwan

	\medskip
	Email: \href{mailto:kwlai@gate.sinica.edu.tw}{kwlai@gate.sinica.edu.tw}\qquad
	Tel.: +886-2-23685999\# 623\\
	Personal website: \url{https://kwlai-math.github.io/}

\medskip


%--------------------
\section*{Empolyment}
\begin{itemize}[itemsep=0pt,parsep=0pt]
	\item[] Academia Sinica, Taiwan
	\begin{itemize}[itemsep=0pt]
		\item[] Postdoc, September~1, 2023--present
	\end{itemize}
	\item[] Universit\"at Bonn, Deutschland
	\begin{itemize}[itemsep=0pt]
		\item[] Postdoc, September~1, 2021--August~31, 2023; part of the ERC Synergy Grant \href{https://doi.org/10.3030/854361}{HyperK (ID: 854361)}.
	\end{itemize}
	\item[] University of Massachusetts Amherst, USA
	\begin{itemize}[itemsep=0pt]
		\item[] Visiting Assistant Professor, September~1, 2018--August~31, 2021
	\end{itemize}
	\item[] Taida Institute for Mathematical Sciences, Taiwan
	\begin{itemize}[itemsep=0pt]
		\item[] Research Assistant, August 2012--July 2013
	\end{itemize}
	\item[] R.O.C. (Taiwan) Army, Taiwan
	\begin{itemize}
		\item[] Obligatory military service, August 2011--July 2012
	\end{itemize}
\end{itemize}


%--------------------
\section*{Education}
\begin{itemize}[itemsep=0pt,parsep=0pt]
	\item[] Brown University, USA
	\begin{itemize}[itemsep=0pt]
		\item[] Ph.D. Mathematics, May 27th, 2018. Thesis: {\it Cremona transformations and rational parametrizations inspired by Hodge theory}, supervised by Brendan Hassett
	\end{itemize}
	\item[] Rice University, USA
	\begin{itemize}[itemsep=0pt]
		\item[] Graduate student, August 2013--July 2015. Transferred to Brown University with Brendan Hassett.
	\end{itemize}
	\item[] National Taiwan University, Taiwan
	\begin{itemize}[itemsep=0pt]
		\item[] M.S. Mathematics, June 4th, 2011. Thesis: {\it The Gromov-Witten Theory of $\varmathbb{P}^1$}, supervised by Hui-Wen Lin
		\item[] B.S. Physics, minor in Mathematics, June 7th, 2009
	\end{itemize}
\end{itemize}


%--------------------
\section*{Research Interests}
Algebraic geometry, especially cubic fourfolds, Cremona transformations, and holomorphic symplectic manifolds.


%--------------------
\section*{Preprints}
\begin{itemize}[leftmargin=!, itemsep=0pt]
	\item On the irrationality of moduli spaces of projective hyperk\"ahler manifolds (with Daniele Agostini and Ignacio Barros), \url{https://arxiv.org/abs/2307.07391}.
	\item Nielsen realization problem for derived automorphisms of generic K3 surfaces (with Yu-Wei Fan), \url{https://arxiv.org/abs/2302.12663}.
	\item Frobenius nonclassical hypersurfaces (with Shamil Asgarli and Lian Duan), \url{https://arxiv.org/abs/2207.11981}.
	\item Transverse linear subspaces to hypersurfaces over finite fields (with Shamil Asgarli and Lian Duan), \url{https://arxiv.org/abs/2008.11306}.
\end{itemize}


%--------------------
\section*{Publications}
\begin{enumerate}[leftmargin=!, itemsep=0pt]
	\item Fourier--Mukai numbers of K3 categories of very general special cubic fourfolds (with Yu-Wei Fan), Israel Journal of Mathematics, accepted.
	\item New rational cubic fourfolds arising from Cremona transformations (with Yu-Wei Fan), \href{https://doi.org/10.14231/AG-2023-014}{Algebraic Geometry 10 (4) (2023), 432--460}.
	\item On the irrationality of moduli spaces of K3 surfaces (with Daniele Agostini and Ignacio Barros), \href{https://doi.org/10.1090/tran/8830}{Transactions of the American Mathematical Society 376 (2023), No.~2, 1407--1426}.
	\item Bijective Cremona transformations of the plane (with Shamil Asgarli, Masahiro Nakahara, and Susanna Zimmermann), \href{https://doi.org/10.1007/s00029-022-00768-0}{Selecta Mathematica, New Series 28, 53 (2022)}.
	\item Uniform potential density for rational points on algebraic groups and elliptic K3 surfaces (with Masahiro Nakahara), \href{https://doi.org/10.1093/imrn/rnab237}{International Mathematics Research Notices 2022, no.~23, 18541--18588}.
	\item Decompositions of Lagrangian classes on K3 surfaces (with Yu-Shen Lin and Luca Schaffler), \href{https://dx.doi.org/10.4310/MRL.2021.v28.n6.a5}{Mathematical Research Letters 28 (2021), no. 6, 1739--1763}.
	\item Transverse lines to surfaces over finite fields (with Shamil Asgarli and Lian Duan), \href{https://doi.org/10.1007/s00229-020-01200-7}{manuscripta mathematica 165, 135--157 (2021)}.
	\item Cremona transformations and derived equivalences of K3 surfaces (with Brendan Hassett), \href{https://doi.org/10.1112/S0010437X18007145}{Compositio Mathematica 154 (2018), no. 7, 1508--1533}.
	\item New cubic fourfolds with odd degree unirational parametrizations, \href{https://doi.org/10.2140/ant.2017.11.1597}{Algebra \& Number Theory 11 (2017), 1597--1626}.
\end{enumerate}


%--------------------
\section*{Other Writings}
\begin{itemize}[leftmargin=!, itemsep=0pt]
	\item A tour of the rationality problem of cubic fourfolds --- an expository article written for the Proceedings of ICCM 2020 as well as a series of lectures from July 28 to August 3, 2021, at Academia Sinica.
\end{itemize}


%--------------------
\section*{Research Talks}
\begin{itemize}[leftmargin=!, itemsep=0pt]
	\item[2024] Taiwanese Mathematical Society (TMS) Annual Meeting, National Chengchi University, January~22--23
	\item[-] Taipei Postdoc Seminar, Academia Sinica \& National Center for Theoretical Sciences (NCTS), January~03
	\item[2023] Student Geometry Seminar, National Tsing Hua University, November~16
	\item[-] Algebraic Geometry in East Asia, Korea Institute for Advanced Study (KIAS), November~06--10
	\item[-] NCTS Seminar in Algebraic Geometry, National Center for Theoretical Sciences (NCTS), September~22
	\item[-] Algebra, geometry and number theory seminar, Universiteit Leiden, April~26
	\item[-] Higher Dimensional Algebraic Geometry Workshop, National Center for Theoretical Sciences (NCTS), March 20--24
	\item[-] Colloquium, National Central University, March~16
	\item[-] Colloquium, National Cheng Kung University, March~09
	\item[2022] Birational Complexity of Algebraic Varieties, Simons Center for Geometry and Physics (SCGP), December 12--16
	\item[-] G\'eom\'etrie Alg\'ebrique et G\'eom\'etrie Complexe, Centre International de Rencontres Math-\'{e}matiques (CIRM), November~28--December~02
	\item[-] Algebraic and Arithmetic Geometry Seminar, Universit\"at Bielefeld, June~01
	\item[-] Colloquium, National Tsing Hua University, March~21 (Online)
	\item[2021] Arithm\'etique et g\'eométrie alg\'ebrique, Universit\'e de Strasbourg, December~09
	\item[-] Seminar Algebraic Geometry, Universit\"{a}t Bonn, November~18
	\item[-] A tour of the rationality problem of cubic fourfolds, Academia Sinica, Taipei, Lecture series during July~28--August~03
	\item[-] Seminar of Algebraic Geometry in East Asia, April~16 (Online)
	\item[2020] International Congress of Chinese Mathematicians (ICCM) at the University of Science and Technology of China, December~27--29 (Online)
	\item[-] Mathematical Physics Seminar, Center of Mathematical Sciences and Applications (CM-SA), April~20 (Online)
	\item[-] Geometry, Physics, and Representation Theory Seminar, Northeastern University, January~23.
	\item[-] Colloquium, National Central University, Taiwan, January~09.
	\item[2019] Front Range Algebraic Geometry and Number Theory (FRAGMENT) seminar, Colorado State University, December~12.
	\item[-] Algebra and Number Theory Seminar, Dartmouth College, September~17.
	\item[-] A Summer Day on Algebraic Geometry, Center for Advanced Study in Theoretical Sciences (CASTS), July~01.
	\item[-] Valley Geometry Seminar, UMass Amherst, March~08.
	\item[-] NT \& AG Seminar, Boston College, February~07.
	\item[2018] Valley Geometry Seminar, UMass Amherst, October~05.
	\item[-] Workshop on Moduli Spaces and Related Problems, Shanghai Center for Mathematical Sciences (SCMS), September~17--21.
	\item[-] Valley Geometry Seminar, UMass Amherst, March~02.
	\item[2017] Mini-talk at Georgia Algebraic Geometry Symposium (GAGS), University of Georgia, March~03--05.
	\item[-] Yale Algebraic and Tropical Geometry, Yale University, February~16.
	\item[-] Princeton Algebraic Geometry Seminar, Princeton University, February~14.
	\item[-] Algebra and Algebraic Geometry Seminars, Brown University, February~10.
	\item[2016] Algebra and Algebraic Geometry Seminars, Brown University, October~14.
	\item[2013] Algebraic Geometry and Number Theory Seminar, Rice University, December~03.
\end{itemize}


%--------------------
\section*{Other Activities}
I have invited and hosted speakers for the following seminars:
\begin{itemize}[leftmargin=!, itemsep=0pt]
	\item[-] Seminar Algebraic Geometry, University of Bonn, Winter 2021--Summer 2023
	\item[-] Valley Geometry Seminar, UMass Amherst, Fall 2018--Spring 2021
\end{itemize}
I have also helped organize the conference:
\begin{itemize}[leftmargin=!, itemsep=0pt]
	\item[-] Algebraic Geometry Northeastern Series, UMass Amherst, March~22--24, 2019
\end{itemize}

I have been invited to review papers or give quick opinions for Canadian Mathematical Bulletin, Crelle's Journal, European Journal of Mathematics, Geometry \& Topology, Journal of Differential Geometry, Mathematische Zeitschrift, Selecta Mathematica, and some proceedings.


\medskip
%--------------------
\section*{Teaching Experience}
\smallskip

{\bf Universit\"at Bonn}
\begin{itemize}[itemsep=0pt]
	\item[2022] Summer Semester, Birational Geometry of Algebraic Varieties
\end{itemize}
{\bf UMass Amherst}
\begin{itemize}[itemsep=0pt]
	\item[2021] Spring, Fundamental Concepts of Mathematics (Two sections)
	\item[2020] Fall, Independent Study on Algebraic Geometry, Andrew Tawfeek
	\item[-] Fall, Fundamental Concepts of Mathematics (Two sections)
	\item[-] Spring, Independent Study on Algebraic Geometry, Andrew Tawfeek
	\item[-] Spring, Fundamental Concepts of Mathematics
	\item[-] Spring, Multivariate Calculus
	\item[2019] Fall, Multivariate Calculus (Two sections)
	\item[-] Spring, Calculus II (Two sections)
	\item[2018] Fall, Calculus I (Two sections)
\end{itemize}
{\bf Brown University}
\begin{itemize}[itemsep=0pt]
	\item[2017] Fall, Intermediate Calculus
	\item[2015] Fall, Introductory Calculus I
\end{itemize}
{\bf Rice University}
\begin{itemize}[itemsep=0pt]
	\item[2015] Summer, Single Variable Calculus II
\end{itemize}


\end{document}



%--------------------Recycle Bin
{\bf Teaching Assistant}
\begin{itemize}[itemsep=0pt]
	\item[2016] Fall, Introductory Calculus II, Brown University
\end{itemize}
During the six semesters from 2013 Fall to 2015 Spring at Rice University,
I'd also been teaching assistants of the following courses
\begin{itemize}[itemsep=0pt]
	\item Single Variable Calculus I
	\item Single Variable Calculus II 
	\item ORD Differential Equations
\end{itemize}


{\bf Earlier Teaching Experiences}
\begin{itemize}[itemsep=0pt,parsep=0pt]
	\item[2007] Summer, Teaching in Remote Areas, Gansu, China.
	\begin{itemize}[itemsep=0pt]
		\item This is an activity organized by \emph{Eden Social Welfare Foundation} of Taiwan.
			We were volunteers forward a remote area in Gansu, China and served as teachers in a junior high school for one week. I designed and taught a series of physics courses.
	\end{itemize}
	\item[2006] Spring, Physics Camp, National Taiwan University.
	\begin{itemize}[itemsep=0pt]
		\item Designed and led a session involving lecture and experiment about a physical concept for senior high school students.
	\end{itemize}
\end{itemize}
